\documentclass[11pt,a4paper,sans]{moderncv}

% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking' 
\moderncvstyle{banking}
% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and  'black'
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.8]{geometry}

% personal data
\name{Gisela}{Morinigo}
\address{Av. Maipu 1855 7D}{Vte. López (CP 1636)}{Bs. As., Argentina}
\phone[mobile]{54-11-5972-0764}
\phone[fixed]{54-11-47955709}
\email{gisemo@gmail.com}
\extrainfo{Passport 29506398N, US VISA B1}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}

\cventry{2000--2006}{System Engineering}{Universidad Tecnológica Nacional, FRBA}{Degree}{}{}
\cventry{2012--Final thesis ongoing}{Software Engineering Specialist}{Universidad Católica de Buenos Aires, FCFI}{Post-Degree}{}{}

\section{Personal objectives}

To find a challenging position to utilize my skills and abilities as Functional/Business/Product Analyst
and Project Leader, to be able to interact with clients and team groups from
different cultures and in diverse countries. 
I am a very analytic person with good communication and problem solving skills. 
I like dynamic environments and I adapt easily to changes.

\section{Skills}

\cvitem{Senior Level}{Requirements elicitation, creating use cases/user
stories/product catalog, managing project status as a project leader, estimations, project scheduling, SQL, UML, Agile
methodology, ms project, user experience, usability, ecommerce business, prepare training for users}

\cvitem{Semi-senior Level}{.NET framework, Java, MS SQL Server, Pascal,
Prolog, SmallTalk, MySQL,  Web Servers, XML, SOA, Drupal, PMBOK Guide (PMI), Object
Oriented Programming}

\cvitem{Junior Level}{Corel Draw, DB2, Dreamweaver, Firework, Hubs \& Switches,
Illustrator, JavaScript, JSP / Servlet / JavaBeans, Linux, SAP, TCP/IP, VPN,
Windows 9x,  Eclipse, Netbeans, Hibernate, Struts, Spring, Nhibernate,
Spring.Net, Design Patterns, Websphere 5.1 , Tomcat, Ruby}



\subsection{Application and tools}

\begin{itemize}
  \item Tools for modeling and documenting software systems: Enterprise Architect, Rational, Power AMC, TFS. (Advance level in modeling using UML)
  \item Tool for issue tracking, task tracking, and project management: Bugzilla, JIRA, Quality Center, TFS.
  \item Tool for sharing information: Confluence, Sharepoint, internal wikis.

\end{itemize}

\section{Languages}

\cventry{}{}{Spanish}{Native}{}{}
\cventry{}{FCE certification}{English}{Fluent}{}{Lived and worked abroad on English-speaking countries. Worked closely with English-speaking stakeholders.}
\cventry{}{Delf A1}{French}{Intermediate}{}{Worked with french-speaking team members. Currently studying the language at Alianza Francesa.}

\section{Activities and Interests}

Member of Scouts de Argentina: leader responsible for the planning of activities.

\section{Experience}
\cventry{09/2011--Present}{Functional Analyst Team Leader \& Product Analyst of Concerto}{AXA Assistance Argentina}{Buenos Aires}{}
{
I started in AXA as a Functional Analyst and I was in charge of elicitation and creating the functional documents of my projects related to changes on the AXA internal product called "Concerto". I also was in charge of the knowledge transfer and follow up of the testers assigned to my projects
\newline{}
Since January 2013, I was promoted to Team Leader and in my team there are 5 analysts.
\newline{}
As Functional Analyst Team Leader, my responsibilities are:
}
\begin{itemize}
  \item Functional responsible of "Concerto" (a .net application developed in Paris and Buenos Aires, it involves the full AXA business process from the call center to billing) 
  \item Propose improvements and new functionalities in Concerto 
  \item Assign the functional analysts of my team in the different projects based on the knowledge and availability
  \item Estimations
  \item Follow up of all analysts' projects in order to meet budget and milestones
  \item Work on the yearly goal of the analysts and in the performance review
  \item Organize training when a new release before a new release is launched
  \item Unblock any member of my team in order to meet deadlines
  \item Create status reports of the analysts' assignments
\newline{}
\end{itemize}



\cventry{02/2011--08/2011}{Senior Business Analyst \& Project Leader}{DIRECTV}{Buenos Aires}{}{
Working in the Regional IT team and my responsibility is to understand the new
processes in order to implement them in all Panamericana region from Directv.
\newline{}}

\cventry{10/2010--01/2011}{Senior Functional Analyst}{Freelancer}{Buenos Aires}{}{I worked for a customer from UK and I was in charge of all functional documentation and change requests of 2 e-commerce sites: Argos and CarpetRight from UK.
\newline{}
Update meetings
\newline{}
Analyze customer’s needs in order to identify business requirements
\newline{}
Create prototypes in order to validate proposals
\newline{}
Follow up the development of my proposals and support to QA and Testers
\newline{}}

\cventry{03/2010--09/2010}{Senior Functional Analyst}{Summit Media (Globant Contractor)}{Prague, Check Republic}{}{I have worked as Functional Analyst abroad for 6 months (in Prague, Czech Republic) and I was in charge of the functional analyst team. The development team was spread all over the world (India, Argentina, UK and Prague).
\newline{}
My responsibility was to elicit requirements and offer different solutions and approaches to solve the business need.
\newline{}
Pre sales support: I had to create Functional Specification and I have participated in estimations
\newline{}}

\cventry{08/2009--02/2010}{Senior Functional Analyst and Project Leader}{IntelligenX}{Buenos Aires}{}{
Methodology: Agile
\newline{}
Writing user stories
\newline{}
Document systems functionalities in APT format in the project
\newline{}
Write user manuals and document business processes
\newline{}}


\cventry{01/2008--07/2009}{Semi Senior Functional Analyst}{Globant}{Buenos Aires}{}{
Methodology: Agile
\newline{}
Extracting requirements and documenting those definitions
\newline{}
Wrote user stories for the projects: GLOW and DNA (both internal projects)
\newline{}
Wrote user manuals
\newline{}
I was the only Functional Analyst in a team of 30 developers (20 in Buenos Aires, 5 in Tandil and 5 in US) and 5 QC Analysts.
The system we built was developed in Java and .Net using an object oriented design
\newline{}
GLOW and DNA Training
\newline{}
Pre sales support: I had to create Functional Specification and I have helped in estimations
\newline{}
In charge of the planning and development of a UML Training Course
\newline{}}


\cventry{06/2005--12/2007}{Java and .Net Developer, Functional Analyst SSr and Project Leader}{Patagonia Technologies}{Buenos Aires}{}{
Extracting of requirements and Functional analysis
\newline{}
Use Case specifications and design of sequence and activity diagrams
\newline{}
User Interface prototype specification and development
\newline{}
Estimating resources 
\newline{}
Follow up meeting and minutes
\newline{}
Development in Java and .net framework
\newline{}
Projects in Patagonia:}

\begin{itemize}
  \item 2006/2007 – Telecom: \newline{}
I was involved in four projects: Gestión de Emprendimientos, Portal de Autogestión, Estadísticas 0800 y Mi Cuenta.
My responsibilities as Functional Analyst are extracting requirements, defining and documenting those business requirements; design use cases using UML;  user Interface prototype specification. Also, as a Project Leader I am responsible for monitoring progress in all project simultaneously.

  \item 2006 –  La Caja de Ahorro y Seguro \newline{}
I was involved in one project: HDLC
My main responsibility was to develop in Java an internal tool for the company. (Eclipse 3.1, Hibernate, Struts)

  \item 2005 – Telecom \newline{}
I was involved in one project: Comisiones
My responsibilities were to extract the requirements, research and prioritize user requirements; Use Case specification and User Interface prototype specification and development.

  \item 2005 – INSA \newline{}
I was involved in one project: Gestor de Residuos
My responsibilities were to analyze user needs to determine functional requirements, functional analysis and design use cases and sequence diagrams.

  \item 2005 – Solis System \newline{}  
I was involved in one project: NEP
My responsibilities were to analyze requirements, use case specification and design of activity and sequence diagrams.
Development in Java (win application using Netbeans).
Development in Visual Studio 2003 .NET
All communication were in English
\newline{}
\end{itemize}


\cventry{03/2004--05/2005}{Data Center analyst}{EDS}{Buenos Aires}{}{
Audit tape process (Data center)
\newline{}
Monitoring bank processes (mainframe, TSO (ispf))
\newline{}
Coordination of technical services
\newline{}
Inventory of modems and crypt devices
\newline{}}

\cventry{06/2003--02/2004}{Administrative Analyst}{LatinGrafica}{Buenos Aires}{}{
Calculate budget (magazines, books, etc)
\newline{}
Negotiate with suppliers}

\clearpage
\end{document}
